Plot-figure-X

### 2018-11-08 code/pacific-figure-andrew-temp/plot-figure-x.Rmd
minor updates on colours

p4 <-  ggplot(merged_whales, aes(x = day_no_f, y = z.d13C.obs)) + 
  facet_wrap(~whale_ID) + 
  geom_line(col = "red") + 
  geom_point(col = "red", size = 1) + 
  geom_line(aes(x = day_no, y = z.d13C.sim), col = "black") + 
  xlab("Day number") + 
  ylab("z-scored d13C")

@@

ggsave("pacific-fits.pdf", plot = p4)
```

>>>>

p4 <-  ggplot(merged_whales, aes(x = day_no_f, y = z.d13C.obs)) + 
  facet_wrap(~whale_ID) + 
  geom_line(col = "black") + 
  geom_point(col = "black", size = 1) + 
  geom_line(aes(x = day_no, y = z.d13C.sim), col = "grey60") + 
  xlab("Day number") + 
  ylab("z-scored d13C") + 
  theme_classic() + 
  theme(strip.background = element_blank())

@@

ggsave("pacific-fits.eps", plot = p4)
```
